\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-30 ase20/eval.tex
Revised 5.3

\begin{table}[t]
  \centering
  \caption{Proposals that will be included in ES11}
  \label{table:spec-prop-result}
  \vspace*{-0.5em}
  \small
  \begin{tabular}{@{}c@{}?r|@{~}r@{~}|@{}c@{}|@{}c@{}|c@{}}
    \multicolumn{1}{@{}c@{}?}{\multirow{2}{*}{\bf Proposal}} &
    \multicolumn{2}{@{~}c@{~}|}{\bf \( \Delta \) \# Prod.} &
    \multicolumn{1}{@{~}c@{~}|}{\multirow{2}{*}{\bf \( \Delta \)\! \#\! Steps}} &
    \multicolumn{1}{@{~}c@{~}|}{\multirow{2}{*}{\bf \( \Delta \)\! \#\! Tests}} &
    \multicolumn{1}{c@{}}{\multirow{2}{*}{\bf \# Tests}} \\\cline{2-3}

@@

    {\bf Total} &
    8 &
    11 &
    502/577 &
  \end{tabular}
\end{table}

\subsection{Forward Compatibility}
We evaluated whether \( \tool \) is forward compatible by applying it
to the proposals that are ready for inclusion in ES11.  Because
ECMAScript is an open-source project, various proposals for new
language features are available with their own specification changes and tests.
A separate repository~\cite{proposals} maintains such proposals with six
stages: Stage 0 to Stage 3, Finished, and Inactive.  A proposal
starts with Stage 0, and the TC39 committee examines proposals in Stage 3.
If a proposal is confirmed, the committee changes
its stage to Finished and integrates it into the next ECMAScript.
Otherwise, the committee changes its stage to Inactive.
Thus, we applied \( \tool \) to all nine proposals in the Finished stage.

Table~\ref{table:spec-prop-result} shows the result of applying \( \tool \) to the
Finished proposals.  Collectively, the proposals modified \inred{XX} lexical and
\inred{XX} syntactic productions, and \( \tool \) successfully
synthesized parsers for them.  The newly synthesized parsers parse all
applicable tests for all proposals.  For abstract algorithms,
\inred{XXX} steps out of \inred{XXX} are automatically converted to
corresponding \( \ires \) instructions by \textsf{Algorithm Compiler}
without changing {\sf Compile Rules}.  Thus, \( \tool \) has the
success rate of \inred{XX.XX\%} on average for forthcoming proposals.

@@

Using the failed tests, we discovered four specification errors in the
BigInt proposal: three new errors (BigInt-1 to BigInt-3) and one known
error (BigInt-4) as summarized in Table~\ref{table:spec-errors}.
All of them were confirmed by TC39 and will be fixed in the next ECMAScript.
The proposal added two new types: BigInt as a new type of primitives
and Numeric as a unified type of the original Number type and the new BigInt type.
Therefore, it not only added new algorithms for BigInt but also modified
all existing algorithms for number values.
The error BigInt-1 is due to a simple misuse of the variable 
\code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.
BigInt-2 and BigInt-3 break the backward compatibility because of
the incorrectly mixed uses of {\bf ToInt32} and {\bf ToUint32}
in unsigned right shift operators and bitwise operators, respectively.
Finally, BigInt-4 happened because the proposal did not consider
BigInt primitives in the Number constructor.  On average, four
specification errors existed for \inred{XXX} days in the proposal.

>>>>

\begin{table}[t]
  \centering
  \caption{Proposals that will be included in ES11}
  \label{table:spec-prop-result}
  \vspace*{-1em}
  \small
  \begin{tabular}{@{}c@{}?r|@{~}r@{~}|@{}c@{}|@{}c@{}|c@{}}
    \multicolumn{1}{@{}c@{}?}{\multirow{2}{*}{\bf Proposal}} &
    \multicolumn{2}{@{~}c@{~}|}{\bf \( \Delta \) \# Prod.} &
    \multicolumn{1}{@{~}c@{~}|}{\multirow{2}{*}{\bf \( \Delta \)\! \#\! Steps}} &
    \multicolumn{1}{@{~}c@{~}|}{\multirow{2}{*}{\bf \( \Delta \)\! \#\! Tests}} &
    \multicolumn{1}{c@{}}{\multirow{2}{*}{\bf \# Tests}} \\\cline{2-3}

@@

    {\bf Total} &
    8 &
    11 &
    502/577 &
  \end{tabular}
\vspace*{-1em}
\end{table}

\subsection{Forward Compatibility}
We evaluated whether \( \tool \) is forward compatible by applying it
to the proposals ready for inclusion in ES11.  Because
ECMAScript is an open-source project, various proposals for new
features are available with their own specification changes and tests.
A separate repository~\cite{proposals} maintains them in six
stages: Stage 0 to Stage 3, Finished, and Inactive.  A proposal
starts with Stage 0, and the TC39 committee examines proposals in Stage 3.
If a proposal is confirmed, the committee changes
its stage to Finished and integrates it into the next ECMAScript.
Otherwise, its stage becomes Inactive.

We applied \( \tool \) to all nine Finished proposals as shown in
Table~\ref{table:spec-prop-result}.
Collectively, the proposals modified \inred{XX} lexical and
\inred{XX} syntactic productions, and \( \tool \) successfully
synthesized parsers for them.  The synthesized parsers parse all
applicable tests for all proposals.  For abstract algorithms,
\inred{XXX} steps out of \inred{XXX} are automatically converted to
corresponding \( \ires \) instructions by \textsf{Algorithm Compiler}
without changing {\sf Compile Rules}.  Thus, \( \tool \) has the
success rate of \inred{XX.XX\%} on average for forthcoming proposals.

@@

Using the failed tests, we discovered four errors in the
BigInt proposal: three new errors (BigInt-1 to BigInt-3) and one known
error (BigInt-4) as summarized in Table~\ref{table:spec-errors}.
All of them were confirmed by TC39 and will be fixed in ES11.
The proposal added two new types: BigInt as a new type of primitives
and Numeric as a unified type of the original Number type and the new BigInt type.
Therefore, it not only added new algorithms for BigInt but also modified
all existing algorithms for number values.
The error BigInt-1 is due to a misuse of the variable 
\code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.
BigInt-2 and BigInt-3 break the backward compatibility because of
misusing {\bf ToInt32} and {\bf ToUint32}
in unsigned right shift operators and bitwise operators, respectively.
BigInt-4 is due to missing BigInt primitives in the Number constructor.
On average, four errors existed for \inred{XXX} days in the proposal.
